\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-18 paper/paper 2/dc-2015.tex
3.5

As stated in Section~\ref{sec:motivation}, we see a huge potential in the possibility to transform semantically equivalent constraints from one high-level constraint language to another via the RDF-CV representation, to avoid that every possible combination of constraint languages has to be mapped separately. The following SPIN inference rule exemplifies this approach and provides a mapping from RDF-CV back to an OWL 2 constraint:

>>>>

As stated in Section~\ref{sec:motivation}, we see a huge potential in the possibility to transform semantically equivalent constraints from one high-level constraint language to another via the RDF-CV representation, to avoid that every possible combination of constraint languages has to be mapped separately. The following SPIN inference rule exemplifies this approach and provides a mapping from RDF-CV back to the OWL 2 constraint of the type \emph{minimum qualified cardinality restrictions}:
